---
title: 健康風險-天氣與精神異常
author: ''
date: '2018-01-07'
slug: ''
categories:
  - Reserch
tags:
  - dlnm
  - health risk assessment
  - mental issue
  - weather effect
  - 非線性遞延模型
  - 健康風險評估
  - 精神異常
  - 天氣
---


```{r 0.library.and.data,warning=F,echo=F,message=F}
setwd("F:/RProject/EMS")
library(data.table)
library(dplyr)
library(dlnm)
library(splines)
library(kableExtra)
library(plotly)
library(knitr)
library(directlabels)
library(ggrepel)

load(file="data/ntp.dlnm.rda")
load(file="data/shorttesrmrisk.rda")
load(file="data/longtesrmrisk.rda")

sub.city.case.hourly=sub.city.case%>%
  mutate(Year=Date%>%format("%Y"),
         Month=Date%>%format("%m"),
         Day=Date%>%format("%d"),
         Week=week(Date),
         DOW=weekdays(Date))%>%
  arrange(Date,Hour)

sub.city.case.daily=sub.city.case%>%
  mutate(Year=Date%>%format("%Y"),
         Month=Date%>%format("%m"),
         Day=Date%>%format("%d"),
         Week=week(Date),
         DOW=weekdays(Date))%>%
  arrange(Date,Hour)%>%
  select(-datetime)%>%
  group_by(Date, Year,Month,Day,Week,DOW)%>%
  summarise(Case=sum(Case),
            ps.mean=ps%>%mean(na.rm=T),
            temp.mean=temp%>%mean(na.rm=T),
            temp.min=temp%>%min(na.rm=T),
            temp.max=temp%>%max(na.rm=T),
            temp.dtr=temp.max-temp.min,
            rh.mean=rh%>%mean(na.rm=T),
            ws.mean=ws%>%mean(na.rm=T),
            rf.sum=rf%>%sum(na.rm=T),
            ss.sum=ss%>%sum(na.rm=T))%>%
  data.frame()
rm(sub.city.case)

myround=function(x){
  x=data.frame(x.num=x,x.log=log10(x)%>%round(digits=1))
  x=x%>%
    mutate(x.char=x.num%>%as.character(),
           x.char=ifelse(x.log>=2,x.num%>%round(digits = 0)%>%as.character(),x.char),
           x.char=ifelse(x.log<2&x.log>=1,x.num%>%round(digits = 1)%>%as.character(),x.char),
           x.char=ifelse(x.log<1&x.log>=0,x.num%>%round(digits = 2)%>%as.character(),x.char),
           x.char=ifelse(x.log<0,x.num%>%round(digits = 2)%>%as.character(),x.char))
  return(x$x.char)
}
```

#1.簡介

本研究主要欲探討的議題為氣象狀況對精神相關疾病之影響。

目前取得因精神異常以致使用緊急醫療救護系統之資料。

研究設定新北市為主要研究區域，時間為2006-2013年。

並使用中央氣象局局屬測站板橋站資天氣時資料，其中包含：氣壓、溫度、濕度、風速、日照時數。

**本篇為個人研究成果，無公開、未發表**

#2.研究方法

##2.1長期暴露分析

  - 使用日資料

  - 探討累積累積30天之**劑量-延遲-反應**病例交叉模型

  - 主要探討影響因子包含：日平均氣壓、日平均溫度、日最低溫度、日最高溫度、日溫差、日平均濕度、日平均風速、日總日照時間
  
  - 調整之因子包含：長期趨勢、周次日期
  
  - 將個別探討主要影響標的影響情形，即一次僅使用一種氣象參數
  
##2.2短期暴露分析

  - 使用時資料

  - 探討累積48天小時之**劑量-延遲-反應**病例交叉模型

  - 主要探討影響因子包含：時溫度
  
  - 調整之因子包含：長期趨勢、周次日期、時濕度、時風速

##2.3模型參數設定

  - 使用非線性遞延廣義線性模式(Distributed Lag Non-Linear Models)
  
  - 利用氣象參數，設定以的二次雲行線(nature cubic spline)擬合的時間-變量二維矩陣。
  
  - 延遲時間與氣象因子二次雲行線的參數設置如：自由度(df)、節點(knots)設置方式首先考量過去文獻、過去經驗、利用赤池信息指標(Akaike information criterion)選出較配適度較高的組合。
  
  - 延遲時間有短期：48小時(時資料)、長期：30天(日資料)兩種，主要考量來自過去文獻提出，在長期趨勢中，極端高溫影響主要集中於前七天，極端低溫的影響則在21天後；而短期暴露的延遲效應較少人提出，需要考證。
  
  - 長期趨勢的調整因子，也利用雲行線設定，因總研究時間為8年，總共設置10*8個自由度，參考自過去文獻。
  
  - 周次日期為類別變數之調整因子；以周一最為參考點。不另外使用節日、流感住院人數為調整因子。
  
  - 短期暴露分析中添加每小時溫度與風速為調整因子，使用自由度為四之雲行線擬合。
  
  - 長期暴露分析中一次只討論一個氣象因子，不考慮兩個氣象因子的模式與交互作用。
  
  - 顯著風險增幅判定是當相對風險(RR)與他的95%信賴區間都大於1。保護效果則是皆小於一。
  
  - 無論何種暴露方式，都使用「累積相對風險」與「特定溫度、時間之相對風險」來觀察時間、主要氣象因子對因精神異常使用救護系統人數之風險。其目的是因為，累積相對風險可以針對總風險進行描述，但沒有詳細說明不同時間、變量的單位風險，當某一因子僅在特定時間點出現風險，總風險不一定會有顯著，因此才會利用特定溫度、時間之相對風險進行描述。

#3.研究成果

##3.1敘述性統計

###3.1.1日資料

######Table.1 Summary table - Daily variable

```{r 3.1.1.summary.table.weather,warning=F,echo=F,message=F}
table.3.1.1=sub.city.case.daily%>%
  select(Case,ps.mean,temp.mean,temp.min,temp.max,temp.dtr,rh.mean,ws.mean,ss.sum)%>%
  melt()%>%
  group_by(variable)%>%
  summarise(`Total Size`=n(),
            `Zero`=ifelse(value==0,1,0)%>%sum(na.rm=T),
            `Missing`=value%>%is.na%>%sum(na.rm=T),
            Sum=value%>%sum(na.rm=T),
            Mean=value%>%mean(na.rm=T)%>%round(digits=2),
            `Standard Deviation`=value%>%sd(na.rm=T)%>%round(digits=2),
            Minimum=value%>%min(na.rm=T)%>%round(digits=2),
            Maximum=value%>%max(na.rm=T)%>%round(digits=2),
            `25th`=value%>%quantile(na.rm=T)%>%.[2]%>%round(digits=2),
            `50th`=value%>%quantile(na.rm=T)%>%.[3]%>%round(digits=2),
            `75th`=value%>%quantile(na.rm=T)%>%.[4]%>%round(digits=2))%>%
  ungroup()%>%
  mutate(variable=c("Patients","Pressure (hpa)","Temperature (C)","Temperature (C)","Temperature (C)","Temperature",
                    "Relative humidity (%)","Wind speed (m/s)","Sun shine (hour)"),
         Method=c("Sum","Mean","Mean","Minimum","Maximum","Differ","Mean","Mean","Sum"))%>%
  mutate_at(.vars = c(5:12),.funs = funs(myround(.)))%>%
  select(variable,Method,`Total Size`:`75th`)%>%
  rename(Names="variable")
table.3.1.1%>%
  kable("html")%>%
  kable_styling(bootstrap_options = "striped", full_width = F)%>%
  add_header_above(c("Variable"=2,"Sample"=3,"Basic index"=5,"Percentiles"=3))
```

######Figure.1 Trend plot - Daily variable

```{r 3.1.1.plot.variable.trend,warning=F,echo=F,message=F,dpi=300,fig.height=10}
sub.city.case.daily%>%
  select(Date,Case,ps.mean,temp.mean,temp.min,temp.max,temp.dtr,rh.mean,ws.mean,ss.sum)%>%
  melt(id.vars=c("Date"))%>%
  mutate(variable=factor(variable,
                         levels=c("Case","ps.mean","temp.mean","temp.min","temp.max","temp.dtr","rh.mean","ws.mean","ss.sum"),
                         labels=c("Patients","Presure","Maen temperature","Minimum temperature","Maximum temperature","Temperature DTR","Mean relative humidity","Mean wind speed","Sum sunshine hour")))%>%
  ggplot(aes(Date,value))+
  geom_point(size=0.5,alpha=0.5)+
  facet_wrap(~variable,ncol=2,scale="free_y")+
  labs(x="Year",y="")+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

######Figure.2 Boxplot - Daily variable

```{r 3.1.1.boxplot.variable.trend,warning=F,echo=F,message=F,dpi=300,fig.height=6}
sub.city.case.daily%>%
  select(Date,Case,ps.mean,temp.mean,temp.min,temp.max,temp.dtr,rh.mean,ws.mean,ss.sum)%>%
  melt(id.vars=c("Date"))%>%
  mutate(variable=factor(variable,
                         levels=c("Case","ps.mean","temp.mean","temp.min","temp.max","temp.dtr","rh.mean","ws.mean","ss.sum"),
                         labels=c("Patients","Presure","Maen temperature","Minimum temperature","Maximum temperature","Temperature DTR","Mean relative humidity","Mean wind speed","Sum sunshine hour")))%>%
  ggplot(aes(x=variable,y=value))+
  geom_boxplot()+
  facet_wrap(~variable,ncol=1,scale="free")+
  labs(x="",y="")+
  coord_flip()+
  theme_bw()+
  theme(strip.background = element_blank(),
        axis.text.y = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

###3.1.2小時資料

######Table.2 Summary table - Hourly variable

```{r 3.1.2.summary.table.ems,warning=F,echo=F,message=F}
table.3.1.2=sub.city.case.hourly%>%
  select(Case,ps,temp,rh,ws,ss)%>%
  melt()%>%
  group_by(variable)%>%
  summarise(`Total Size`=n(),
            `Zero`=ifelse(value==0,1,0)%>%sum(na.rm=T),
            `Missing`=value%>%is.na%>%sum(na.rm=T),
            Sum=value%>%sum(na.rm=T),
            Mean=value%>%mean(na.rm=T)%>%round(digits=2),
            `Standard Deviation`=value%>%sd(na.rm=T)%>%round(digits=2),
            Minimum=value%>%min(na.rm=T)%>%round(digits=2),
            Maximum=value%>%max(na.rm=T)%>%round(digits=2),
            `25th`=value%>%quantile(na.rm=T)%>%.[2]%>%round(digits=2),
            `50th`=value%>%quantile(na.rm=T)%>%.[3]%>%round(digits=2),
            `75th`=value%>%quantile(na.rm=T)%>%.[4]%>%round(digits=2))%>%
  ungroup()%>%
  mutate(variable=c("Patients","Pressure (hpa)","Temperature (C)","Relative humidity (%)","Wind speed (m/s)","Sun shine (hour)"))%>%
  mutate_at(.vars = c(4:11),.funs = funs(myround(.)))%>%
  select(variable,`Total Size`:`75th`)%>%
  rename(Names="variable")
table.3.1.2%>%
  kable("html")%>%
  kable_styling(bootstrap_options = "striped", full_width = F)%>%
  add_header_above(c("Variable"=1,"Sample"=3,"Basic index"=5,"Percentiles"=3))
```

###3.1.3各類因子與使用救護系統人數分布

####3.1.3.1時間

######Figure.3 Annually trend of patients

```{r 3.1.3.1.Annually.line.cahrt,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.daily%>%
  group_by(Year)%>%
  summarise(Case=sum(Case,na.rm = T))%>%
  ggplot(aes(x=Year%>%as.numeric(),y=Case))+
  geom_line(colour="#023852",size=1.5)+
  geom_point(fill="#023852", colour="white",pch=21, size=4,stroke = 4)+
  geom_text(aes(label=paste(Case,"\n",round(Case/sum(Case)*100,digits=1),"%",sep="")),vjust=-0.2)+
  labs(x="年度",y="")+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.text.y = element_blank())
```

######Figure.4 Annually patients number in each months

```{r 3.1.3.1.barchart.month,warning=F,echo=F,message=F,dpi=300,fig.height=8}
sub.city.case.daily%>%
  group_by(Year,Month)%>%
  summarise(Case=sum(Case,na.rm = T))%>%
  ggplot(aes(x=Month,y=Case))+
  geom_bar(stat="identity",fill="#DBA67B",colour="white",size=2)+
  geom_text(aes(label=paste(Year,"\n","N=",Case,sep="")),vjust=2,position = "stack",colour="#023852",size=3)+
  labs(x="",y="")+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom")
```

######Figure.5 Box plot for Patients number in day of week

```{r 3.1.3.1.boxplot.dow,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.daily%>%
  mutate(DOW=factor(DOW,levels=c("星期日","星期一","星期二","星期三","星期四","星期五","星期六")))%>%
  ggplot(aes(x=DOW,y=Case))+
  geom_boxplot()+
  labs(x="",y="")+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

####3.1.3.2氣象因子

######Figure.6 Bar plot - Cases in temperature

```{r 3.1.3.2.Case.in,each.temperature,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.hourly%>%
  select(temp,Case)%>%
  mutate(temp=round(temp))%>%
  group_by(temp)%>%
  summarise(Case=sum(Case),
            Days=n())%>%
  ungroup%>%
  mutate(Case.percent=Case/sum(Case)*100)%>%
  ggplot(aes(x=temp))+
  geom_bar(aes(y=Case.percent,fill="Patients"),stat="identity")+
  geom_line(aes(y=Case/Days*10,colour="#EAE7D6"),size=1.5)+
  geom_point(aes(y=Case/Days*10,fill="PerDay", colour="#EF525B"),pch=21, size=1,stroke = 1)+
  scale_fill_manual(values=c("#082E41", "#DA2536"),labels = c("Case number(%)","Case per 10 days"))+
  scale_colour_manual(values=c("#EAE7D6","#EF525B"))+
  labs(x="Temperature",y="Patient(%)",fill="")+
  guides(colour=F)+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom")
```

######Figure.7 Contour plot - Cases in relative humidity

```{r 3.1.3.2.Case.in,each.relative.humidity,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.hourly%>%
  select(rh,Case)%>%
  mutate(rh=round(rh))%>%
  group_by(rh)%>%
  summarise(Case=sum(Case),
            Days=n())%>%
  ungroup%>%
  mutate(Case.percent=Case/sum(Case)*100)%>%
  ggplot(aes(x=rh))+
  geom_bar(aes(y=Case.percent,fill="Patients"),stat="identity")+
  geom_line(aes(y=Case/Days*10,colour="#EAE7D6"),size=1.5)+
  geom_point(aes(y=Case/Days*10,fill="PerDay", colour="#EF525B"),pch=21, size=1,stroke = 1)+
  scale_fill_manual(values=c("#082E41", "#DA2536"),labels = c("Case number(%)","Case per 10 days"))+
  scale_colour_manual(values=c("#EAE7D6","#EF525B"))+
  labs(x="Relative humidity",y="Patient(%)",fill="")+
  guides(colour=F)+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        legend.position = "bottom")
```

######Figure.8 Contour plot - Cases in temperature and relative humidity

```{r 3.1.3.2.Annually.line.cahrt,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.hourly%>%
  select(temp,rh,Case)%>%
  mutate(temp=round(temp),
         rh=round(rh))%>%
  group_by(temp,rh)%>%
  summarise(Case=sum(Case))%>%
  ggplot(aes(x=temp,y=rh,,z=Case))+
  geom_tile(aes(fill=Case))+
  geom_contour()+
  geom_smooth(colour="#EF525B",se=F)+
  labs(x="Temperature",y="Relative humidity")+
  scale_fill_gradient2(low="#FFEC97",mid="#60A65F",high="#2B3D54")+
  theme_bw()+
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

######Figure.9 Point distrebuted - Temperature and Pressure

```{r 3.1.3.2.point.temp.ps,warning=F,echo=F,message=F,dpi=300,fig.height=4}
sub.city.case.daily%>%
  select(ps.mean,temp.mean)%>%
  ggplot(aes(x=temp.mean,y=ps.mean))+
  geom_smooth()+
  geom_point(alpha=0.5,size=0.5)+
  labs(x="Mean temperature",y="Pressure")+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

##3.2氣象因子風險模型

###3.2.1長期暴露

####3.2.1.1日平均氣壓

######Figure.10 Significant cumulative relative risk of long-term daily mean ambient pressure exposures on lag 30 days.

```{r 3.2.1.1.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ps.mean")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Mean ambient pressure (hpa)",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.11 Significant cumulative and specific relative risk of long-term daily mean ambient pressure exposures on lag 0 to 30 days.

```{r 3.2.1.1.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ps.mean")%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Mean ambient pressure (hpa)",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  scale_x_continuous(limits=c(971,1032))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

####3.2.1.2氣溫

#####3.2.1.2.1日平均氣溫

######Figure.12 Significant cumulative relative risk of long-term daily mean temperature exposures on lag 30 days.

```{r 3.2.1.2.1.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.mean")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Mean temperature",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.13 Significant cumulative and specific relative risk of long-term daily mean temperature exposures on lag 0 to 30 days.

```{r 3.2.1.2.1.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.mean")%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Mean temperature",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  scale_x_continuous(limits=c(8,32))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

#####3.2.1.2.2日最低氣溫

######Figure.14 Significant cumulative relative risk of long-term daily minimum temperature exposures on lag 30 days.

```{r 3.2.1.2.2.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.min")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  scale_x_continuous(limits=c(5,30))+
  scale_y_continuous(limits=c(0,30))+
  labs(x="Minium temperature",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.15 Contour - Significant cumulative and specific relative risk of long-term daily minimum temperature exposures on lag 0 to 30 days.

```{r 3.2.1.2.2.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.min")%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Minium temperature",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

#####3.2.1.2.3日最高氣溫

######Figure.16 Significant cumulative relative risk of long-term daily maximum temperature exposures on lag 30 days.

```{r 3.2.1.2.3.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.max")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Maximum temperature",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.17 Significant cumulative and specific relative risk of long-term daily maximum temperature exposures on lag 0 to 30 days.

```{r 3.2.1.2.3.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.max")%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Maximum temperature",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  scale_x_continuous(limits=c(9,39))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

#####3.2.1.2.4日溫差

######Figure.18 Significant cumulative relative risk of long-term diurnal temperature range exposures on lag 30 days.

```{r 3.2.1.2.4.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.dtr")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Diurnal temperature range",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**下圖均不顯著**

######Figure.19 Cumulative and specific relative risk of long-term diurnal temperature range exposures on lag 0 to 30 days.

```{r 3.2.1.2.4.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="temp.dtr")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Diurnal temperature range",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FCFFF5",high="#CBDBD7")+
  scale_x_continuous(limits=c(0,19))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

####3.2.1.3日平均濕度

######Figure.20 Significant cumulative relative risk of long-term mean relative humidity exposures on lag 30 days.

```{r 3.2.1.3.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="rh.mean")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Average relative humidity (%)",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "bottom",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.21 Significant cumulative and specific relative risk of long-term mean relative humidity exposures on lag 0 to 30 days.

```{r 3.2.1.3.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="rh.mean")%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Average relative humidity (%)",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  scale_x_continuous(limits=c(39,97))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

####3.2.1.4日平均風速

######Figure.22 Significant cumulative relative risk of long-term mean wind speed exposures on lag 30 days.

```{r 3.2.1.4.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ws.mean")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Mean wind speed (m/s)",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "none",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**下圖均不顯著**

######Figure.23 Cumulative and specific relative risk of long-term mean wind speed exposures on lag 0 to 30 days.

```{r 3.2.1.4.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ws.mean")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Mean wind speed (m/s)",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FCFFF5",high="#CBDBD7")+
  scale_x_continuous(limits=c(0,7))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

####3.2.1.5日總日照時間

######Figure.24 Significant cumulative relative risk of long-term total sunshine hour exposures on lag 30 days.

```{r 3.2.1.5.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ss.sum")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==30)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Total sunshine hour (hour)",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "none",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**下圖均不顯著**

######Figure.25 Cumulative and specific relative risk of long-term total sunshine hour exposures on lag 0 to 30 days.

```{r 3.2.1.5.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr.long%>%
  filter(ind.variable=="ss.sum")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Total sunshine hour (hour)",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FCFFF5",high="#CBDBD7")+
  scale_x_continuous(limits=c(0,13))+
  scale_y_continuous(limits=c(0,30))+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

###3.2.2短期暴露

######Figure.26 Significant cumulative relative risk of short-term hourly temperature exposures on lag 48 hours.

```{r 3.2.2.RR.overall,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr%>%
  filter(ind.variable=="Temp")%>%
  filter(RRtype=="Cmulative predicted associations",Lagtpye==48)%>%
  mutate(RR=paste(myround(fit)," (",myround(low),"-",myround(high),")",sep=""),
         RR=ifelse(Significant=="Significant",RR,""))%>%
  ggplot(aes(x=ind.variable.value,y=fit,ymin=low,ymax=high))+
  geom_hline(yintercept = 1,linetype = 2,colour="#ED1B4B",size=1)+
  geom_ribbon(fill="#F2D06B",alpha=0.3)+
  geom_line(colour="#A8226B",alpha=1)+
  geom_point(fill="#023852", colour="white",pch=21, size=2,stroke = 1,aes(alpha=Significant))+
  geom_label_repel(aes(label=RR),fill=0.5)+
  scale_alpha_manual(values=c(0,1))+
  labs(x="Total sunshine hour (hour)",y="Relative risk",alpha="")+
  theme_bw()+
  theme(legend.position = "none",
        strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

```

**僅呈現有顯著之風險**

######Figure.27 Significant cumulative and specific relative risk of short-term daily hourly temperature exposures on lag 0 to 48 hours.

```{r 3.2.2.RR.countour,warning=F,echo=F,message=F,dpi=300,fig.height=4}
list.rr%>%
  filter(Significant=="Significant")%>%
  ggplot(aes(x=ind.variable.value,y=Lagtpye))+
  geom_tile(aes(fill=fit))+
  geom_contour(aes(z=fit),colour="#52003B",binwidth = 0.25)+
  facet_grid(~RRtype)+
  labs(x="Temperature",y="Lag hours",fill="Relative risk")+
  scale_fill_continuous(low="#FFC286",high="#945634")+
  theme_bw()+
  theme(strip.background = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())
```

